---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WashEx

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/washex)](https://CRAN.R-project.org/package=washex)
[![R-CMD-check](https://github.com/rwrandles/washex-r/workflows/R-CMD-check/badge.svg)](https://github.com/rwrandles/washex-r/actions)
[![Travis build status](https://travis-ci.com/rwrandles/washex-r.svg?branch=main)](https://app.travis-ci.com/rwrandles/washex-r.svg?branch=main)
<!-- badges: end -->

The **Wash**ington **Ex**plorer (WashEx) package creates an interface between R and the [Washington State Legislative Web Services](http://wslwebservices.leg.wa.gov). It serves as a companion to [Legislative Explorer: Washington](http://legex.org/wa/process), a project developed by John Wilkerson and Rohnin Randles at the University of Washington. The package contains functions to retrieve data regarding the following:

  * Bill summaries
  * Roll calls
  * Amendments
  * Sponsors
  * Committees
  * Committee membership
  * Hearings
  * Revised Code of Washington (RCW)

## Installation

You can install the released version of `washex` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("washex")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rwrandles/washex-r")
```

## Usage

Some possible implementations of the `washex` package include

```{r example, message=FALSE, warning=FALSE}
library(washex)
library(tidyverse)

sponsors_2007 <- getSponsors("2007-08")
sponsors_2007 %>% 
  group_by(District) %>%
  summarize(prop_repub = round(mean(Party == "R"),3))

head(getCommittees("2007-08")[,"Name"])

head(getStatusChanges("2007-08", "1001") %>%
  select("HistoryLine", "ActionDate"))

ag_bills <- getRCWBills("2007-08", c("15","16"))
getRollCalls.votes("2007-08", ag_bills$BillNumber) %>% 
  filter(str_detect("Final Passage", Motion)) %>%
  mutate(Party = sponsors_2007$Party[match(MemberId, sponsors_2007$Id)]) %>%
  group_by(BillId) %>%
  summarize(repub_support = sum(Vote == "Yea" & Party == "R") / sum(Party == "R"),
            dem_support = sum(Vote == "Yea" & Party == "D") / sum(Party == "D"))
```

## Issues

If you encounter any bugs or issues while using the package, please file an issue with a minimum reproducible example on [Github](https://github.com/rwrandles/washex-r/issues)
